### 2017-06-01 paper.tex
Regularizing name

Thinking systematically about difficulty levels can help manage expectations.
For example,
the Programming Historian project labels lessons ``beginner''",
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
However,
this only works if there is prior agreement on what those terms mean.

>>>>

Thinking systematically about difficulty levels can help manage expectations.
For example,
Programming Historian project labels lessons ``beginner''",
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
However,
this only works if there is prior agreement on what those terms mean.
